\courseeval[Creative Programming]{CS-236}{2010F}{Creative Programming Workshop}{\CS}{createprog}

\subsubsection*{Course Description}
In this course students will work on collaborative programming projects,
using programming tools and methodologies presented in class. The course
will include topics from software engineering, graphics, and functional
programming, but will be focused on student-directed, faculty-mentored
programming projects. Students will program continuously and read, run,
and criticize on another's programs. These programs may be written
for any application area and may include utilities, games, artworks,
cognitive models, and environmental or social simulations. We will
develop the ability to critique programs from a variety of perspectives
ranging from complexity theory to aesthetics. Prerequisite: one
programming course (in any language). This course satisfies Division I
distribution requirements. PRJ, PRS, QUA

\subsubsection*{Instructor Narrative}
Alec's performance in this class was mixed. He was one of the most
proficient and engaged programmers in the class, and he clearly mastered
the material that we covered while working on a range of personal
projects including an AI search algorithm, a termite colony simulator,
and a simulator for the "prisoner's dilemma" economic game. Alec gave
an excellent presentation to the class on ways to combine two of the
programming tools that we were using, and he was exceptionally helpful
in class discussions and in collaborative coding sessions. On the other
hand he missed several classes at the end of the semester, he failed to
give a final presentation, and he provided insufficient documentation
with his final portfolio. Nonetheless, Alec clearly demonstrated strong
computer science skills in this course and I believe that he learned
a fair amount through his participation. I look forward to seeing his
future work.
