\courseeval{TA-CS (CS-109)}{2012F}{Programming Creativity}{\TA}{createprog-ta}

\subsubsection*{Course Description}
This course is an introduction to computer science and programming
framed by the question, Is it possible for a computer to be creative?"
The core areas of computer science will be introduced, including
algorithms, complexity, computability, programming languages, data
structures, systems, and artificial intelligence, with an eye toward the
insights that they can provide about issues of computational creativity.
Students will complete several programming projects to demonstrate
developing technical skills and engagement with the themes of the
course." Cumulative Skills: QUA, IND

\subsubsection*{Instructor Narrative}
Alec was the sole teaching assistant for this introductory computer
science course and his duties included attending class regularly,
helping students during in-class coding sessions, helping to administer
in-class presentations, answering student questions during office hours
and by email, and helping to organize submitted student work.
 
This was a particularly challenging teaching assistantship because
the students in the class had an unusually wide range of backgrounds
and because many students had ambitious project ideas that required
the rapid acquisition of new programming skills. Alec worked hard and
consciously to help all students who approached him, but the conditions
of the class made it inevitable that he would sometimes provide students
with more new information than they could digest, or put students on a
path that they could not complete on their own. Alec appreciated these
difficulties, he mitigated them to the best of his ability, and he wrote
about them intelligently in his self-evaluation. In the end, despite
these difficulties, it is clear to me that Alec did an excellent job of
helping students, and that many of the students in the class owe much of
their success to Alec's help. Alec's performance on his other duties --
helping me, rather than the students -- was uniformly excellent. In sum,
Alec did a great job on this difficult assignment, and I was very happy
to have his assistance.
