\courseeval{CS-0236}{2010F}{Application-Oriented Database Theory}{\CS}{databases}

\subsection*{Course Description}
Application-Oriented Database Theory: Databases are ubiquitous in
society -- there are few websites, applications or devices you encounter
on a daily basis that aren't tied to a database. This course will
examine the history and theory of databases starting with E.F. Codd
as "the father of relational databases" from his groundbreaking
work published in 1970 through the current state with the "usual
suspects" (mysql, oracle, MSSQL) coupled with some less known players
(Unidata/Universe, Cache', OpenQM, jBase...) This is not a course in
mysql. This is a course where we'll play and plan on getting our hands
dirty. Students will be expected to do reading/research on assigned
topics and presenting them in class for discussion. Likewise, students
should be prepared to use some of these databases and objectively look
at their merits as well as shortcomings. PRJ, PRS, QUA

\subsection*{Instructor Narrative}
Alec's work in this course was very good. Unlike many in the course, he
arrived with a strong background in databases so Alec spent more of his
time working independently, coming to me with questions that were more
advanced than most in the course might've been able to grasp.

In short, Alec's work was excellent. He completed the work requested and
went much further than others in an attempt to investigate databases
other than mysql for some of his personal interests.
