\courseeval[Pygame Course]{TA-CS-2 (CS-112)}{2012S}{Teaching Assistant - Programming Games - Introduction to Programming Using Python and Pygame}{\TA}{pygame-ta}

\subsection*{Course Description}
Programming Games: Introduction to Programming using Python and Pygame: This is
an introductory programming course that will motivate programming through the
creation of videogames using the Pygame libraries for Python. Students will
learn the basics of programming in Python and then quickly move to creating
games. New programming concepts will be introduced as a means to further game
creation. Basic concepts in videogame design will also be introduced. By the
end of the course, students will have learned how to program and will have
written multiple games. No previous programming experience is required.

\subsection*{Instructor Narrative}
Alec Goebel was the lead teaching assistant for CS112 an introductory
programming course in Python that used Pygame and game development to motivate
learning to program. In this roll he organized the other TAs, did the majority
of the grading, held lab hours, and developed class examples and homework
assignments. In addition he attended class and helped students during class
time. Where Alec really excelled was in his contributions to the lectures. He
both added insights to material presented in class and taught the 3 lectures
when I was out of town. Alec was the glue that held this course together and
without his efforts the course could not have happened. He did have a little
trouble meeting deadlines for preparing material but this was outweighed by his
overall effort. Alec was a phenomenal TA for this course.
