\courseeval[Video Game Design 2]{CS-360}{2010F}{Video Game Design 2: Continuing Building Video Games from Scratch}{\IMGD}{vgdesign2}

\subsubsection*{Description}
This course is the continuation of CS260 Video Game Design. It focuses
on video game theory and active development of games whereas CS260
focused on the introduction of tools. Students will use their knowledge
to lead groups of current CS260 students while actively participating
in the development process. This course will also focus on development
of games for the iPhone/iTouch platform. Prerequisite: Students are
required to have taken CS260 Video Game Design.

\subsubsection*{Instructor Narrative}
Alec's performance in this course was generally good. His work on the
individual assignments at the beginning of the semester was superb and
he managed to push the software we were using beyond the scope expected
by its designers. Alec's work on the group final project varied.

Alec was the group member who built the game engine and essentially
built the game. Alec's programming of the game was enough beyond his
group mates that this seemed like a reasonable plan. Unfortunately when
Alec missed a couple of weeks of class it threw his group into disarray
and left his group mates with nothing to work on until he reappeared. If
Alec had been willing to trust his group mates with more of the project
and had kept in communication a little better the project would have run
a lot smoother.

One crucial detail is that in the game post-mortem Alec and his group
recognized this issue. Alec was the first to say that it was his actions
that caused the greatest issues with group dynamics. As a group they
were able to recognize where their group dynamics failed and were able
to discuss possible ways of fixing them for future group work. This
ability to recognize and address issues is crucial in game design and
other fields and is a big success for Alec.

Ultimately they were able to build a successful game and thus succeeded
in the course. Alec did well but could have been the strongest student
in the course and needs to work on his communication.
