\section{Creative Programming (2 evals)}

\begin{meta}
    \mitem{Course}{TA-CS-5, CS-236}
    \mitem{Term}{2012 Fall, 2010 Fall}
    \mitem{Prof}{Lee Spector}
    \mitem{Lang}{Clojure}
    \mitem{Lib}{quil}
\end{meta}

\courseself
\subsubsection*{Student}
As with many of my other courses in Fall 2010, being back in college as
an experienced programmer was interesting. I already knew Lisps and had
worked briefly with Clojure the summer before.

The problem that plauged me during the course is one I still wrestle
with at Hampshire: scope creep. In attempts to challenge myself in new
and interesting ways I would come up with projects which in reality
would take me several months to do as a full time job. As a result, I
bounced between ideas and never really settled on anything I wanted to
work on AND had time to work on. In the end, I only turned in the toy
processing problems I had created to get used to atoms.

The big regret I have for this course is not finishing my Google Code
Jam parser DSL. It was a way to rapidly parse out the input files into
variable bindings. I got caught with nested macros or some other strange
bug.


\subsubsection*{Teaching Assistant}
Looking at this course from the other side reinforced how I was expecting
too much from myself the last time around. The projects most of the
students were working on were ones I could do in an afternoon. And often
did.

For TAing this class I tried making functional prototypes of people's
work on my own before I spoke with them to get a better idea on how they
should approach the problem. This wound up being a double edged sword.
On one hand, my thoughts were clearer and I didn't stumble through an
explanation, figuring it out as I went. On the other hand, it was
harder for me to change paths on the fly to go with a simpler solution
for a student having more trouble.

Overall, I think I did well as TA. Despite sometimes helping too much
I'm confident students were still learning from what we did together.
Going forward, I'll probably try to give students a best guess on how
to make something and send them off to work while I try implementing it
on my own. This should allow for a more immediate discussion, give them
time to get started, and give me time to figure out where they will probably
get stuck.


\loadtex[\vfill]{evals/creative-programming-ta}
\loadtex{evals/creative-programming-student}
