\section{Researching Gamification and DSLs}

\begin{meta}
    \mitem{Course}{IS-CS-200-3}
    \mitem{Term}{2012 Spring}
    \mitem{Prof}{Paul Dickson}
\end{meta}

\subsection*{Self Eval}
This study shifted a fair amount over the semester. Originally I
was trying to design a system to quickly create game elements for
Hampshire campus. This would be things like CASA being able to give
out achievements to mark one's progress through the divisional system.
Clubs could quickly generate challenges for their members. As I figured
out more aspects, I attempted to create the design for an easy to use
interface for non-technical users.

As the year went on, the design became unwieldy so I shifted my focus
down to how the system would work for a single course. Taking elements
of game design, I worked out a way for text book material to be laid out
in an "explorable" graph. In addition, I spent a lot of time planning
how small homework assignments would work so students couldn't actually
fail them while still being challenged.

The one thing I noticed was that although a little research had been
done, I could find very little information on the area I was looking
for. Though people had documented how to create badges, I could find no
simple ways to create to layout a "game world" out of an N-dimensional
graph.

Overall, I'm proud of the results. I am currently about 10 pages
into the specification documentation, with many times more notes and
thoughts. Though this was originally my intended Div 3, as I thought
more about it over the summer I realized the project was a bit nebulous
and vague. It was hard to imagine having something I was proud to show
off in a year, especially with my current experience level. At some
point I'd like to work more on it, but not now.

\loadtex[\vfill]{evals/gamification}
