\section{Pygame Course (4 evals)}

\begin{meta}
    \mitem{Courses}{CS200-7, CS200, TA-CS-2, CS-300-3}
    \mitem{Prof}{Paul Dickson}
    \mitem{Terms}{2011 Fall, 2012 Jan, 2012 Spring}
    \mitem{Lang}{Python}
    \mitem{Lib}{Pygame}
\end{meta}

\subsection*{Self Eval}
This course was my "first div 3". It was the primary thing I was working
on the entire school year. First, I roughly planned out the curriculum
as an independent study. Over Jan term I taught Pygame to the other
TA's and Paul, as well as fleshing out the actual in class examples and
homework assignments. Then, in the spring I TA-ed and ran an advanced
section on Fridays.

Although I program all the time, I don't think I have ever written
so much for a single project before. I created turnin scripts, step
by step versions of the in class examples, the homeworks assignments
(including ones for the advanced section), and unit tests to grade some
of the homework assignments. When the class moved on to final projects,
I created several small samples to show how to create platformers,
cameras, and menus. By the end of the class, I had a working final
project of my own (Super Coin Get) and a multiplayer beta (Super Coin
Get Madness).

I pushed myself a little too hard on the time commitment. In addition
to attending each class and sticking around after, I held about 10 lab
hours a week (my days from 6-12 and the other TA's days.) Then it was
back to writing new class examples and the homework for the next week.

In addition to doing a substantial amount of the prep work, I taught a
Friday addendum course and on occasion when Paul was out. The advanced
section was mixed, and we covered a wide range of things: from design
patterns to python nicities. Still, almost everyone in the advanced
section created wonderful things for their final using some of the
techniques we covered. It wasn't what I planned, but it worked out.

Overall, the course was flawed but it was a good first run. There are
so many things I'd do differently were I to get the chance to teach
it again. I'd slow the pace, replace some of the examples, get rid of
github entirely, etc.

This course was the most rewarding part of my education to date and
something I am truly proud of, especially when I see how far some
students have come since they started.

\loadtex[\vspace{0.75in}]{evals/pygame-design}
\loadtex[\vfill]{evals/pygame-prep}\vspace{1in}
\loadtex{evals/pygame-addendum}
\loadtex[\vfill]{evals/pygame-ta}

