\section{Video Game Design 2}

\begin{meta}
    \mitem{Course}{CS-360}
    \mitem{Term}{2010 Fall}
    \mitem{Prof}{Paul Dickson}
    \mitem{Lang}{Javascript}
    \mitem{Tools}{Cabana}
\end{meta}

\courseself
I have mixed feelings about the results of this course. On one hand, I
am mostly proud of what I accomplished. I was able to create a variety
of libraries to work around Cabana's limitations. In Cabana itself I
created a variety of fun widgets that even the developers took notice
of. I also created decent Javascript game engine and level generator
framework. Most importantly, I improved upon how I go about making games
from scratch; I started with a decent modular framework in mind instead
of just hacking it bit by bit.

However, this was my worst performance as a group member. There were
a few contributing factors. First, I was completely out of practice
with school work since this was the first semester back in 2 1/2 years.
Second, my personal life had a huge hiccup halfway through the semester.
Third, I was again trying to challenge myself which meant I took on too
much and made things too complicated for the others. Worst of all was
just my hubris. There was no question I had more experience with game
development than my group, but instead of working with them I decided to
"it would be faster to do it myself."

There comes a point where my ambition is more of a hindrance to myself
and others. I have since gotten a bit better at trusting others with my
code and working with others at their pace. Still, it is something I am
constantly working on.

\loadtex{evals/video-game-design-2.tex}
