\chapter{Other}

% TODO
% hs
% wpi/helpdesk/cablevision
% gdc
% time off


================================================================================
    HIGH SCHOOL
================================================================================

My div 2 really started in high school. I started programming in the 9th
grade. I spent most of it programming games in blender, pygame, and on
my TI83+. In hindsight, I was already spending more time on interfaces
than on the games themselves, creating level editors, tweaking menus,
and adding animations to simple programs.

My junior year, I took AP computer science. This was when I really
learned basic OO and Java. Then, in my senior year I essentially was a
TA for the AP computer science class. That year I won General Electric's
state wide computer science contest. As the prize for first, I could
take one free course at Fairfield University. I wound up in Software
Engineering which was a UML/OO Design course.



% Chapter 2
% 
% 
% Chapter 3
% Various
% 
% High School
% 
% Started web development on my own, eventually took a DHTML course.
% Took AP Java, got a 5
% father’s influence
% Taught myself python, made games made games in blender made games
% on my TI-83+
% Fairly fluent in Java. Had studied a bit of UML. Fairly confident in my
% ability to use python.
% placed 3rd as a junior, 1st as a senior 1st in CS contest. Awarded the
% first ever CS award from HS.


Working with various help desks and online support

cablevision


Talking with non-techies really imporoved my 

Consequence of learning how people go about their lives is finding little ways to improve it.  life hacking, excel macros, small projects around the house linux install is just big personal project always.
Worked actively with WPI's Game Development Club




Was elected president for my last term there.  In my admittedly brief time we held a few game jams, including a 38 hours one for the defunct 38 studios.  For that one we hosted schools from around NE, I ran a crash course in pygame development the week before.  And was a success

Also worked closely with the IMGD faculty and committee to help shape the direction the program was going.  Involved briefly in faculty search.

Acted as mentor and support for various students. 
